### 2023-03-27 response-to-audit-report.md

> **File `MoneyPreservation.thy`, lemma `moneyInInput_is_positive`, line *53***
> 
> The proof could be more general with `apply (cases x; simp)` instead of using `metis`.
> 
> **File `MoneyPreservation.thy`, lemma `reductionLoop_preserves_money_NoPayment_not_ReduceNoWarning`, line *434***
> 
> This lemma can be proved directly with `metis reductionLoop_preserves_money_NoPayment`, and reversing the order in which the lemmas are defined.
> 
> **File `TimeRange.thy`, lemma `inIntervalIdempotentToIntersectInterval`, line *5***
> 
> The lemma can use a shorter proof: `apply (cases min2;cases max2;auto) done`.
> 
> **File `TimeRange.thy`, lemma `inIntervalIdempotency1, inIntervalIdempotency2`, lines *20, 36***
> 
> These lemmas use the `smt` tactic and `metis` where a simpler Isar proof would work, for example:
> 
> ``` text
>   lemma inIntervalIdempotency1 :
>     assumes "inInterval (x, y) (intersectInterval b c)"
>     shows "inInterval (x, y) b"
>   proof (cases b)
>     case [simp]:(Pair b1 b2)
>     thus ?thesis proof (cases c)
>       case (Pair c1 c2)
>       thus ?thesis using assms by (cases c1; cases c2; cases b1;cases b2; simp)
>     qed
>   qed
> ```
> 
> **File `SemanticsGuarantees.thy`, `Various lemmas/instantiations`**
> 
> Multiple lemmas and `linorder` instantiations in this file repeat auxiliary facts within the proof that are not necessary. For example, in the `linorder` instantiation for `Party`, lines 51--53 state
> 
> ``` {.text escapeinside="||" mathescape="true"}
>   have "(x < y) = (x |$\le$| y |$\land$| |$\neg$| y |$\le$| (x :: Token))"
>     by (meson less_Tok.simps less_Token_def less_eq_Token_def linearToken)
>   thus "(x < y) = (x |$\le$| y |$\land$| |$\neg$| y |$\le$| x)" by simp
> ```
> 
> This can be rewritten to avoid repeating the fact as
> 
> ``` {.text escapeinside="||" mathescape="true"}
>   show "(x < y) = (x |$\le$| y |$\land$| |$\neg$| y |$\le$| (x :: Token))"
>     by (meson less_Tok.simps less_Token_def less_eq_Token_def linearToken)
> ```
> 
> This pattern appears many times in this file. For example, in the `Party` instantation alone, it is present on lines 51 -- 53, 56 -- 57, 77 -- 80, and 83 -- 84.

### 2.3.23 Inconsistent style when applying constructor *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemmas `beforeApplyAllLoopIsUseless, fixIntervalOnlySummary`, lines *275, 398***
> 
> The lines mentioned in these lemmas display the resulting constructor before the function application, which differs from the general style in the rest of the codebase.

### 2.3.24 Unsimplified boolean formulas *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemma `computeTransactionIterative_aux2`, lines *708, 710***
> 
> In multiple places, this lemma formulation includes top-level negation in front of nontrivial conjunctions and disjunctions. These negations should be distributed. Otherwise, the reader is taxed with the chore to mentally distribute the negation to understand the lemma.

### 2.3.25 Typo with "independet" in multiple lemmas *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemmas `applyAllLoop_independet_of_acc_error1, applyAllLoop_independet_of_acc_error2`, lines *977, 987***
> 
> In both of these lemmas, there is a typo with the word "independet".

### 2.3.26 Poorly named `acc` lemmas *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemmas `applyAllLoop_independet_of_acc_error1, applyAllLoop_independet_of_acc_error2`, lines *977, 987***
> 
> It is unclear what `acc` refers to in these lemma names, as the lemmas are about the independence of warnings and payments, not accounts.

### 2.3.27 Verbose lemma statement `playTraceAuxIterative_base_case` *(Severity: Low)*

> **File `SingleInputTransactions.thy`, lemma `playTraceAuxIterative_base_case`, line *1063***
> 
> The statement of this lemma is very verbose. A more natural (and slightly stronger) formulation could be $$\begin{aligned} &\mathit{playTraceAux}\ \mathit{txOut}\ [\ \llparenthesis \mathit{interval} = \mathit{inte}, \mathit{inputs} = [h] \rrparenthesis, \llparenthesis \mathit{interval} = \mathit{inte}, \mathit{inputs} = t \rrparenthesis \ ] \\ =\ &\mathit{playTraceAux}\ \mathit{txOut}\ [\ \llparenthesis \mathit{interval} = \mathit{inte}, \mathit{inputs} = h\ \#\ t \rrparenthesis \ ]\end{aligned}$$

### 2.3.28 `playTrace_only_accepts_maxTransactionsInitialState` not written as `theorem` *(Severity: Low)*

> **File `TransactionBound.thy`, lemma `playTrace_only_accepts_maxTransactionsInitialState`, line *316***
> 
> This lemma seems like the main result of this file. Assuming it is an important result, we recommend writing it as a `theorem` rather than a `lemma`.

### 2.3.29 Inconsistent style with assumptions *(Severity: Low)*

> **File `Timeout.thy`, lemmas `timedOutReduceContractUntilQuiescent_closes_contract, timedOutReduceContractStep_empties_accounts`, lines *201/204, 211/214***
> 
> These lemmas use the hypothesis $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ and build a state $\mathit{sta}\ \llparenthesis \mathit{minTime} := \mathit{iniTime} \rrparenthesis)$ while other lemmas simply say $\mathit{minTime}\ \mathit{sta} = \mathit{iniTime}$. Readability would be improved by presenting these lemmas in the same style as the others, or documenting the need for these distinct presentations via code comments.

### 2.3.30 Function `validTimeInterval` unnecessarily unfolded in lemma *(Severity: Low)*

> **File `TimeRange.thy`, lemma `reduceStep_ifCaseLtCt_aux`, line *234***
> 
> For consistency, $a \leq b$ should be replaced by $\texttt{validTimeInterval}$.

### 2.3.31 Overly specific auxiliary lemma *(Severity: Low)*

> **File `ValidState.thy`, lemma `reductionLoop_preserves_valid_state_aux`, line *73***
> 
> This lemma on its own is very specific, and is only used in `reductionLoop_preserves_valid_state`. If possible, we recommend this lemma to be generalized or broken down into smaller lemmas, in order to present the arguments to the reader in smaller pieces.

### 2.3.32 `playTrace_preserves_valid_state` not written as `theorem` *(Severity: Low)*

> **File `ValidState.thy`, lemma `playTrace_preserves_valid_state`, line *194***
> 
> This lemma seems like the main result of this file. Assuming it is an important result, we recommend writing it as a `theorem` instead.

### 2.3.33 Unnecessary assumptions *(Severity: Low)*

> **File `PositiveAccounts.thy`, lemmas `addMoneyToAccountPositive_match, addMoneyToAccountPositive_noMatch`, lines *12, 23***
> 
> The assumptions $$\forall x\ \mathit{tok}.\ \mathit{positiveMoneyInAccountOrNoAccount}\ x\ \mathit{tok}\ \mathit{accs}$$ in `addMoneyToAccountPositive_match` and $$\mathit{money > 0}$$ in `addMoneyToAccountPositive_noMatch` are unnecessary.
> 
> **File `PositiveAccounts.thy`, lemma `reduceContractStep_gtZero_Refund`, line *93***
> 
> The lemma has an assumption that is mostly redundant.
> 
> ``` {.text escapeinside="||" mathescape="true"}
>   Reduced
>     ReduceNoWarning
>     (ReduceWithPayment (Payment party (Party party) tok2 money))
>     (state|$\llparenthesis$|accounts := newAccount|$\rrparenthesis$|) Close
>     =
>   Reduced wa eff newState newCont
> ```
> 
> A stronger lemma would be valid, which results from eliminating the assumption and changing the conclusion to `positiveMoneyInAccountOrNoAccount y tok3 newAccount`.
> 
> **File `QuiescentResult.thy`, lemma `reduceContractStepPayIsQuiescent`, line *17***
> 
> The assumption $\mathit{cont} = \texttt{Pay}\ \mathit{x21}\ \mathit{x22}\ \mathit{tok}\ \mathit{x23}\ \mathit{x24}$ is unnecessary.
> 
> **File `Timeout.thy`, lemma `timedOutReduce_only_quiescent_in_close_When`, line *43***
> 
> The assumption $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ is unnecessary.
> 
> **File `Timeout.thy`, lemma `timedOutReduce_only_quiescent_in_close`, line *122***
> 
> The assumption\ $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ is unnecessary. However, removing it will require the later proof `timedOutReduceContractLoop_closes_contract` to be adjusted.
> 
> **File `Timeout.thy`, lemma `timedOutReduceContractLoop_closes_contract`, lines *170, 173***
> 
> The assumptions $\mathit{minTime}\ \mathit{sta} \leq \mathit{iniTime}$ and $\mathit{minTime} \mathit{sta} = \mathit{iniTime}$ are both present. The former is redundant.
> 
> **File `TimeRange.thy`, lemma `reduceStep_ifCaseLtCt_aux`, line *234***
> 
> The assumption\ $\mathit{env} = \llparenthesis \mathit{timeInterval} = (a, b) \rrparenthesis$ is unnecessary.
> 
> **File `ValidState.thy`, lemma `reductionStep_preserves_valid_state_Refund`, line *29***
> 
> The assumption $$\begin{aligned} \mathit{newState} = \llparenthesis &\mathit{accounts} = \mathit{newAccounts}, \mathit{choices} = \mathit{newChoices}, \\ &\mathit{boundValues} = \mathit{newBoundValues}, \mathit{minTime} = \mathit{newMinTime} \rrparenthesis\end{aligned}$$ is unnecessary.

## 2.4 Isabelle implementation

### 2.4.1 Variable shadowing in `applyAllLoop` *(Severity: Medium)*

> **File `Semantics.thy`, function `applyAllLoop`, line *575***
> 
> The $\texttt{cont}$ variable introduced by the pattern match shadows another $\texttt{cont}$ variable, coming from the pattern match of an outer case expression, making the function harder to follow while also making it more error-prone to future changes.

### 2.4.2 Undescriptive name `moneyInPayment` *(Severity: Low)*

> **File `MoneyPreservation.thy`, function `moneyInPayment`, line *5***
> 
> The name of the function can be more precise. Perhaps `moneyInPaymentToParty` or `moneyInExternalPayment` would work.

### 2.4.3 Typo in section name *(Severity: Low)*

> **File `OptBoundTimeInterval.thy`, line `37`** 
> 
> Typo in section name: "Interval intesection".

### 2.4.4 Typo in comment *(Severity: Low)*

> **File `OptBoundTimeInterval.thy`, line `42`** 
> 
> Typo in comment: "endpoits".

### 2.4.5 Unclear need for multiple formulations for positive accounts *(Severity: Low)*

> **File `PositiveAccounts.thy`, `Throughout`** 
> 
> It is unclear what the use is for multiple formulations (and lemmas about) positive accounts. The first formulation (with the theorems `playTraceAux_gtZero` and `playTrace_gtZero`) is not used in any other modules but the alternative formulation is used instead. If both formulations are relevant, then it should be explained why.

### 2.4.6 Variable name discrepancy in `reductionLoop` *(Severity: Low)*

> **File `Semantics.thy`, function `reductionLoop`** 
> 
> When comparing this function against `specification-v3-rc1.pdf`, different names are used for a let-bound variable. It is `a` in the pdf and `newPayments` in the file `Semantics.thy`. There are similar issues in the function `reduceContractStep` in the equation for the `If` case, and in the function `giveMoney`.

### 2.4.7 Typo in constructor *(Severity: Low)*

> **File `Semantics.thy`, function `applyCases`, line *505***
> 
> Apparent typo in the error message constructor: the party mentioned should be $\texttt{party2}$.

### 2.4.8 Unclear function name `calculateNonAmbiguousInterval` *(Severity: Low)*

> **File `Semantics.thy`, function `calculateNonAmbiguousInterval`, line *725***
> 
> The meaning of the function is not obvious. It needs a comment to explain it.

### 2.4.9 Non-modularized file `SingleInputTransactions.thy` *(Severity: Low)*

> **File `SingleInputTransactions.thy`, `Splitting File`** 
> 
> This file is very long, and it covers more than just single-input transactions. For instance, about 530 lines at the beginning are rather dedicated to idempotence of certain operations. Then, the lemmas around lines 530 -- 700 focus on "well-foundedness" of the recursion on contract steps. Then there is also a clear block of lemmas about "distributivity" of semantics over transaction lists.
> 
> Splitting the module, grouping the related lemmas, would help understanding the relationships between the groups.

### 2.4.10 Misleading function names *(Severity: Low)*

> **File `SingleInputTransactions.thy`, function `inputsToTransactions`, line *9***
> 
> This function name is not very descriptive of its meaning. It takes a transaction (both a time interval and a list of inputs) and returns a list of transactions at the same interval containing a single input each. A name like `splitTransactionIntoSingleInputTransactions` would convey better what the input and the output are.
> 
> Moreover, the code would be cleaner if the function takes a single argument of type `Transaction`, instead of asking the caller to rip apart its fields.
> 
> **File `SingleInputTransactions.thy`, function `traceListToSingleInput`, line *18***
> 
> This function name is not descriptive of what it does. Perhaps a more telling name could be `splitTransactionsIntoSingleInputTransactions`.
> 
> **File `SingleInputTransactions.thy`, function `isSingleInput`, line *1222***
> 
> This function should be renamed or repurposed. If renamed, `allAreSingleInput` more accurately reflects the meaning of the function. If repurposed, it should check that a single transaction has a single input, and `all isSingleInput` can be used to express the current behavior.

### 2.4.11 Unused parameter in `maxTransactionCaseList` *(Severity: Low)*

> **File `TransactionBound.thy`, function `maxTransactionCaseList`, line *16***
> 
> This function has a parameter of type `State` that is completely unused and can be removed.

### 2.4.12 Duplicated `isValidInterval` function *(Severity: Low)*

> **File `TimeRange.thy`, function `isValidInterval`, line *231***
> 
> This function duplicates $\texttt{validTimeInterval}$ from $\texttt{OptBoundTimeInterval.thy}$, and the latter has certain additional properties proven about it specifically, so it makes sense to use the latter in both cases.

## 2.5 marlowe-cardano specification

### 2.5.1 Lack of guidelines for creating cooperating contracts *(Severity: Medium)*

> **File `marlowe-cardano-specification.md`, Section `Life Cycle of a Marlowe Contract`** 
> 
> Given that transactions are expected to work with Marlowe and non-Marlowe contracts simultaneously, it would be helpful to offer some guidelines for other contracts to avoid double satisfaction. Some degree of cooperation between the contracts that can appear in the same transaction is unavoidable.
> 
> One measure could be to ask every cooperating contract to refrain from paying to the payout validator. In this way, double satisfaction can not affect the payments of the Marlowe contract, if the Marlowe contract only pays to roles rather than addresses.
> 
> Another alternative would be to demand other contracts' outputs to use datums that are different from the roles used by the Marlowe contract for payments.

### 2.5.2 No reference to creating a minting policy *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Monetary Policy for Role Tokens`** 
> 
> The minting policy is not specified, but a reference needs to be offered to explain how to create one.

### 2.5.3 Argument for Contract in `txInfoData` not specified *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Types`** 
> 
> The argument by which the `Contract` in the `txInfoData` list corresponds to the given hash needs to be made explicit.

### 2.5.4 Merkleization section not detailed enough *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Merkleization`**
> 
> This section is too terse. It needs to explain what Merkleization is, and to motivate why it is needed.
> 
> When explaining how it works, it needs to make explicit that only the `Case` type is modified, and that in the semantics, only the `Input` type is modified. It needs to explain why the `Input` type needs to carry a hash and a contract, and why the evaluation of the contract is changed as described.

### 2.5.5 Unnecessary constraint *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, `Constraint 12. Merkleized continuations`** 
> 
> This constraint is unnecessary to have in the Marlowe validator, since the construction of the arguments for evaluation of the Marlowe contract would fail. However, it would be useful to have it appear in the specification for users to be aware of it when crafting transactions. A note to motivate the presence of the constraint could be helpful.

### 2.5.6 Asymmetry between role and wallet payouts *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, `Constraint 15`, **
> 
> The marlowe validator allows multiple outputs to be paid to a wallet, but it demands that a single output exists when paying to a role instead. The motivation to use different approaches needs to be documented. This is implemented in `Scripts.hs` at line 371, in function `payoutConstraints`.

### 2.5.7 Incorrect description of `rolePayoutValidator` *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Plutus Validator for Marlowe Payouts`** 
> 
> The description of the Marlowe payout validator in the specification states that it is parameterized by the currency symbol. However, this is not correct as the validator is unparameterized; rather, the datum type of the validator includes the currency symbol (as well as token name). The description should be modified to reflect this.

### 2.5.8 Unspecified initial state *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Life Cycle of a Marlowe Contract`** 
> 
> The specification should say what the initial state of a Marlowe contract should be. In particular, creating a contract requires giving the minimum Ada to some account in the Marlowe state. Otherwise, Constraint 5 will reject the transactions that try to spend the output.

### 2.5.9 Unspecified behavior when multiple cases can apply *(Severity: Low)*

> **File `Semantics.hs`, Function `applyCases`, line *597***
> 
> If multiple cases in a case list can apply, the first one is taken. This behavior should be better communicated in the specification.

## 2.6 Haskell implementation

### 2.6.1 Name shadowing in `applyAllInputs` *(Severity: Medium)*

### 2023-03-27 response-to-audit-report.md

> **File `Semantics.hs`, Function `applyAllInputs`, line *658***
> 
> The binding `cont` from the `Applied` constructor shadows the `cont` variable coming from the pattern match in an enclosing case expression. This makes the code error-prone to subsequent changes and refactorings.

### 2.6.2 Non-isomorphic types in `playTraceAux` *(Severity: Medium)*

> **File `Semantics.hs`, Function `playTraceAux`, line *710***
> 
> The function in the Isabelle code takes a `TransactionOutputRecord` while the Haskell version takes a `TransactionOutput`. This means `TransactionError` cannot be an input to `playTraceAux` in Isabelle, possibly invalidating proofs about its properties.

### 2.6.3 Variable names differ from Isabelle code *(Severity: Low)*

> **File `Semantics.hs`, Several functions ``** 
> 
> Different variable names in Isabelle and Haskell make comparison harder. It is less of an issue when only one variable has been renamed in a function, but multiple variable renames require carefully mapping between the names to avoid confusion. For example, the code of `reduceContractStep` in line 482 (`Pay` case) is hard to compare.
> 
> Other name changes include:
> -   Line 456, function `updateMoneyInAccount` uses variable `money` where the Isabelle code uses `amount` and omits naming the last parameter.
> -   Line 473, function `giveMoneyToPay` uses variables `amount` and `accounts` instead of `money` and `accountsV` as in the Isabelle code.
> -   Line 541, function `reductionLoop` uses variable `con` instead of `ncontract`.
> -   Line 300, the data type `TransactionInput` corresponds to the type `Transaction` in the Isabelle code.
> -   Line 313, the data type `TransactionOutput` is isomorphic but not identical to the homonymous data type in the Isabelle code.
> -   Line 439, function `refundOne` uses a variable `balance` where the Isabelle code uses `money`.
> -   Line 463, function `addMoneyToAccount` uses variable `accounts` where the Isabelle code uses `accountsV`.

### 2.6.4 Naming of functions and variables *(Severity: Low)*

> **File `Several files`, `several functions`** 
> 
> Several functions or variables could have more descriptive or precise names, for example:
> -   `Scripts.hs:193`: `validateBalances` could be called `allBalancesArePositive`.
> -   `Scripts.hs:206`: `validateInputs` could be called `allInputsAreAuthorized`.
> -   `Scripts.hs:324`: `checkScriptOutputAny` could be called `noOutputPaysToOwnAddress`, as it checks that *no* outputs pay to the script address.
> -   `Semantics.hs:439`: `refundOne` is named somewhat confusingly, and understanding the name requires the context of `reduceContractStep` where the function is called. Perhaps a better name would be `dropWhileNonPositiveAndUncons`.
> -   `Semantics.hs:597`: the binding `tailCase` should rather be named `tailCases`.

### 2.6.5 Unused functions *(Severity: Low)*

> **File `Several files`, `several functions`** 
> 
> Several functions are unused and perhaps should be removed:
> -   `Semantics.hs:741`: `contractLifespanUpperBound` does not seem to be used anywhere, including tests.
> -   `Semantics.hs:680`: `isClose` is not used in the rest of the codebase (besides checking its behavior via testing). It should either be removed, or comments justifying its existence should be included.
> 
> In addition to that, the functions `validateBalances` and `totalBalance` (defined at `Semantics.hs:755` and `:762`) are only used in `Scripts.hs` and never reused, so they should probably be moved to `Scripts.hs`.

### 2.6.6 Comments *(Severity: Low)*

> **File `Semantics.hs`, Function `refundOne`, line *439***
> 
> The comment describing the function is overly concise, as it does not mention the function removing all non-positive accounts before the first positive one, and effectively `uncons`-ing the list.
> 
> **File `Semantics.hs`, Function `addMoneyToAccount`, line *461***
> 
> There is a typo in the comment: `accoun` is written instead of `account`.

### 2.6.7 Record updates in `playTraceAux` *(Severity: Low)*

> **File `Semantics.hs`, Function `playTraceAux`, line *710***
> 
> The function could have followed the Isabelle code more closely if it used a record update instead of creating a new `TransactionOutput` record from scratch.

### 2.6.8 Potential simplifications *(Severity: Low)*

> **File `Semantics.hs`, Function `totalBalance`, line *755***
> 
> The function uses `foldMap f . AssocMap.toList`. Here, `AssocMap.toList` is redundant.

> **File `Types.hs`, Class instance `Eq Contract`, line *873***
> 
> The equality of cases for the `When` constructor would be simplified by using `cases1 == cases2`. If there is a reason for the more verbose equality condition, it should be outlined in a comment.

### 2.6.9 `computeTransaction` differs from the Isabelle implementation *(Severity: Low)*

> **Helper function `evalValue, evalObservation`, lines *391 (Semantics.hs), 34 (Semantics.thy)***
> 
> `evalValue` and `evalObservation` differ from the Isabelle implementation in the introduction of auxiliary variables to abbreviate the recursive calls. The comparison would be simpler if both definitions were consolidated.
> 
> **Helper function `evalValue`, lines *395 (Semantics.hs), 35 (Semantics.thy)***
> 
> The Isabelle implementation should use the helper function `moneyInAccount` instead of inlining its definition, so as to maintain consistency with the Haskell implementation.
> 
> **Helper function `applyCases`, lines *596 (Semantics.hs), 498 (Semantics.thy)***
> 
> The structure of function `applyCases` differs between the Haskell and Isabelle files. Specifically, the Haskell implementation has an additional function `applyAction` where the Isabelle implementation does not. A comment motivating the discrepancy would be needed. This is likely due to the lack of Merkleization in the Isabelle implementation.
> 
> **Helper function `convertReduceWarnings`, lines *617 (Semantics.hs), 537 (Semantics.thy)***
> 
> The Haskell function is implemented using `foldr`, while the Isabelle function uses explicit recursion, making a one-to-one comparison less obvious. If there is a reason for this discrepancy, such as `foldr` yielding some optimizations, this should be outlined in a comment.

### 2.6.10 Constraint implementations differ from description *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Plutus Validator for Marlowe Semantics`** 
> 
> Some constraints mentioned in the specification are written in a different structure than the corresponding constraint in `Scripts.hs`. While such a discrepancy may be useful to minimize verbosity, a unified structure when possible would alleviate a side-by-side comparison. Examples of these differing structures include Constraint 6 and Constraint 14.

### 2.6.11 Missing argument of `computeTransaction` *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Section `Relationship between Marlowe Validator and Semantics`** 
> 
> The specification mentions the output datum as the (fifth) argument for the `computeTransaction` function, while it is not an argument to it.

### 2.6.12 Missing `smallMarloweValidator` *(Severity: Low)*

> **File `marlowe-cardano-specification.md`, Various sections ``** 
> 
> The specification mentions `smallMarloweValidator` in a few places, but it is never mentioned in the source code.

### 2.6.13 Incorrect constraint reference *(Severity: Low)*

> **File `Scripts.hs`, Function `mkRolePayoutValidator`, line *150***
> 
> This line should refer to Constraint 17 rather than Constraint 16.

### 2.6.14 `MarloweParams` differs from the specification *(Severity: Low)*

> **File `Semantics.hs`, type `MarloweParams`, line *355***
> 
> The specification defines `MarloweParams` to contain just the payout validator hash, while the definition in the Haskell code contains just the roles currency symbol.

### 2.6.15 Timeout boundary differs from the specification *(Severity: Low)*

> **File `Semantics.hs`, type `reduceContractStep`, line *518***
> 
> The specification mentions
> 
> > If a valid Transaction is computed with a TimeInterval with a start time bigger than the Timeout t, the contingency continuation c is evaluated.
> 
> where "bigger" implies strict inequality, while the code makes non-strict comparison. This difference needs to be acknowledged and further explained in the specification.

## 2.7 Haskell tests

### 2.7.1 More precise failure checks *(Severity: Medium)*

> **File `Spec/Marlowe/Plutus/Specification.hs`, `Various tests`** 
> 
> The tests use the functions `checkSemanticsTransaction` and `checkPayoutTransaction` to verify that various error conditions cause transactions to be rejected. These functions test that a transaction passes or fails, but when it fails, the functions do not consider the error cause. Checking the exact cause is necessary to ensure the transaction is rejected because of the intended reason and not because of some other error condition arising in a particular test case by coincidence.
> 
> The absence of this information makes it easier to accidentally produce a test that is not testing what is intended.

### 2.7.2 Missing tests *(Severity: Medium)*

> **File `Spec/Marlowe/Semantics/Compute.hs`, ``** 
> 
> The following properties could additionally be tested for `computeTransaction`:
> -   payment subtracts from an account,
> -   deposit adds to an account,
> -   `INotify` input produces the expected continuation,
> -   `IChoice` input produces the expected continuation,
> -   the hash of a successfully applied merkleized input matches the hash of the merkleized case.
> 
> Some of these are tested in `Spec/Marlowe/Semantics/Functions.hs` already for auxiliary functions.
> 
> **File `Spec/Marlowe/Semantics/Functions.hs`, `Missing merkleization tests`** 
> 
> The properties in this module do not seem to be tested with merkleized contracts or inputs except for `checkGetContinuation`. More merkleization tests should be added.
> 
> **File `Spec/Marlowe/Semantics/Compute.hs`, function `checkFixInterval`, lines *100-102***
> 
> The test `checkFixInterval` is never instantiated with an invalid interval that is in the past, meaning the function `fixInterval` is never tested for that case.
